An Experimental Evaluation of Hybrid Querying on Vectors (EA\&B)

### 2025-07-30 VLDB2026/main.tex
Update main.tex

	\includegraphics[width=0.95\textwidth]{figures/exp/exp_3_1.pdf}
	\caption{
		 \centering
		Effect of Attribute Distribution on Query Performance \\
		(Strong: robust to attribute distribution shifts; Weak: sensitive to attribute distribution shifts.)}

>>>>

	\includegraphics[width=0.95\textwidth]{figures/exp/exp_3_1.pdf}
	\caption{
		Effect of Attribute Distribution on Query Performance(Strong is robust to attribute distribution shifts, Weak is sensitive to attribute distribution shifts.)}
